The paper on blockchain front-running

### 2018-09-25 frontrunning/Latex/sections/paper.tex
Ok on pause for now

Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be build at the DApp level as seen here.

\paragraph{Design Decision \#1: Commit / Reveal.} \label{CommitmentScheme}
A commitment scheme is a cryptographic primitive that enables one to commit to a value (\eg a statement, document, data, \etc) while keeping it a secret and open it (and only it) at a later time of the commiter's choosing~\cite{brassard1988minimum}. The commitment scheme is a robust method to prevent information leakage from the sensitive transactions. This could be done by simply submitting the hash value of the committed data to a smart contract and later on revealing the values linked to the committed hash, see Figure~\ref{fig:commitReveal}. 
In the case of decentralized exchanges, the user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, the user sends reveal transaction revealing the order details which will be executed in a fair order. This method is not perfect, depending on the DApp design, either the order is collateralized, that means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be vulnerable to Denial-of-Service attacks. 
Another use of such a commitment scheme is in decentralized naming systems, such as Namecoin, Ethereum Name Service (ENS). In this case, a user sends a commit transaction, which commits to the name hash, similar to a sealed bid. Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running. A similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known. 
Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design. On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction. In the ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible thereafter. Also, this scheme means two transactions are required for a functionality which makes it more expensive.

@@

\paragraph{Design Decision \#2: Submarine Commitments.}\label{submarineCommits}
Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized. With submarine send, it is possible to hide sender, receiver, value, and data, the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.

The details of how Submarine commitments work is outside the scope of this paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address of which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}. However, this could be designed in other ways to suit the need of the DApp. Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.

@@

\item \emph{Eliminating Time-Order Dependency:} The applications can be designed not to rely on the time for the orders to be executed. For example when designing a decentralized exchange, one can use \emph{the call market} design instead of a time-sensitive order book. In a call market design, the arrival time of the orders does not matter as they are executed in batches~\cite{clark2014decentralizing}.

\item \emph{Disincentivizing Front-running Actors:} This solution, which is economic rather than technical, is to disincentives the miners by paying them the fees. If the application is designed in a way that the fees of the orders are sent to the miner of the block, he would have less incentive to front-run the orders as he already gains enough financial benefit from acting fairly and executing the transactions on their correct order. For example, Malinova~\cite{malinova2017market} proposes a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable.

@@

Going back to Table~\ref{tab:top25DApps}, some DApps facilitate different methods to mitigate front-running issues. As an example, LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:code}), hence removing any possibility of replay attack or the possibility of any other address sending the similar order. \textblue{is this not its own entry?}

>>>>

Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be built at the DApp level as seen here.

\paragraph{Design Decision \#1: Commit / Reveal.} \label{CommitmentScheme}
A commitment scheme is a cryptographic primitive that enables one to commit to a value (\eg a statement, document, data, \etc) while keeping it a secret, and then open it (and only it) at a later time of the committer's choosing~\cite{brassard1988minimum}. A common approach is to submit the hash value of the data to be committed, potentially with a random nonce (for predictable data), to a smart contract and later reveal the original data and nonce which can be verified to hash to the commitment. See Figure~\ref{fig:commitReveal} in Appendix~\ref{app:cr}.

An early use of commit/reveal is Namecoin, a Bitcoin-forked blockchain for name services~\cite{kalodner2015empirical}. A user sends a commit transaction, which commits to the name hash, similar to a sealed bid. Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.

In the case of decentralized exchanges, users can use commit/reveal for bids, where commitments are placed in an ordered queue and executed in a later round after a reveal. This mitigation seems to require further research. One trader strategy is to flood orders at the commitment stage, but then only selectively and adaptively choose which to reveal. Collateralization is another challenge, where revealed bids may simply be intentions to execute but additional transactions are required to move the money or tokens; a transaction that can also be aborted early. One mitigation to early aborts is having users post a fidelity bond that can be automatically dispensed if they fail to fully execute committed transactions (as used in~\cite{} \textblue{Cite paddy's paper on boardroom voting on ethereum}). Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}. Using sealed votes, voters can make sure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.

Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design. On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction. In the ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible thereafter. Also, this scheme means two transactions are required for a functionality which makes it more expensive.

@@

\paragraph{Design Decision \#2: Submarine Commitments.}\label{submarineCommits}
Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} extend basic commit/reveal functionality with additional properties. In particular, they hide the DApp being invoked during the commit phase and also ensure that revealed transactions that send funds are fully collateralized. With submarine send, it is possible to hide sender, receiver, value, and data, the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants. The details of how Submarine commitments work could fill an entire paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality, it is possible to generate one outgoing transaction from an address of which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase. By revealing the details and broadcasting the constructed transaction we reveal the commitment~\cite{libsubmarine}. See Figure~\ref{fig:LibSubmarine}. However, this could be designed in other ways to suit the need of the DApp. Drawbacks of this scheme are similar to commit/reveal, with the addition of two more transactions to finalize a transaction, which adds cost and complexity to the user experience.

@@

\item \emph{Eliminating Time-Order Dependency:} The applications can be designed not to rely on the time for the orders to be executed. For example when designing a decentralized exchange, one can use a \emph{the call market} design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running by miners. In a call market design, the arrival time of orders do not matter as they are executed in batches.

\item \emph{Disincentivizing Front-running Actors:} The call market solution also pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run. To the same end, Malinova~\cite{malinova2017market} propose a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable. \textblue{this is what it does, how does it do it?}

\item \emph{\textblue{Technique}:} LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:code}), hence removing any possibility of replay attack or the possibility of any other address modifying key information in the order. \textblue{how does this solve front-running?}

@@
